Men and Women Both Prefer and Perceive Inaction as More Competent

### 2024-02-16 outputs/paper/paper.qmd
paper update
Added reproduction link

---
title: "Men and Women Both Prefer and Perceive Inaction as More Competent" 
subtitle: "An Analysis of Preference and Perceived Competence of Actions and Inaction Agents in Risky Decisions Resulting in Negative Outcomes by Gender"
author: 
- Francesca Ye 
- Sky Suh 
- Hari Lee Robledo
date: "today"
date-format: long
abstract: "This report investigates differences between gender and perceptions of action versus inaction agents from research conducted by Adrien et al. Focusing on preference and perceived competence this report graphed the frequencies of responses by gender in addition to statistical analysis. This report found there are no significant differences in preference and perceived competence by gender as both slightly leaned towards inaction for both estimands. Considering the larger field of moral judgment, this report indicates that gender does not seem to be a  strong influence on decision-making approaches as previously thought."
thanks: "Code and data from this analysis are available at: https://github.com/hari-lr/Preference-and-Perception-of-Decision-Making"
toc: true
number-sections: true
bibliography: references.bib
format: pdf
---

@@

[@sec-data] of this report aims to discuss the characteristics of the Study 2 data set examined in addition to the methods of cleaning applied to get workable data for this report. This report’s [@sec-results] highlights trends discovered through graphical analysis in tandem with statistical analysis of the preference and perceived competence responses using t-tests and p-values to determine statistical insignificance. [@sec-discussion] notes possible analytical limitations and measurement errors in the data sets in addition to overall insights of the report’s analysis. Specific discussion will surround the validity of assigning utilitarianism as a trait of men in addition to addressing whether or not there are differences in decision-making approaches based on gender. {@sec-future} aims to explore further research that could be conducted in this field based on the findings presented in this report.

>>>>

---
title: "Men and Women Both Prefer and Perceive Inaction as More Competent" 
subtitle: "An Analysis of Preference and Perceived Competence of Actions and Inaction Agents in Risky Decisions Resulting in Negative Outcomes by Gender"
author: 
- Francesca Ye 
- Sky Suh 
- Hari Lee Robledo
date: "today"
date-format: long
abstract: "This report investigates differences between gender and perceptions of action versus inaction agents from research conducted by Adrien et al. Focusing on preference and perceived competence this report graphed the frequencies of responses by gender in addition to statistical analysis. This report found there are no significant differences in preference and perceived competence by gender as both slightly leaned towards inaction for both estimands. Considering the larger field of moral judgment, this report indicates that gender does not seem to be a  strong influence on decision-making approaches as previously thought."
thanks: "Code and data from this analysis are available at: https://github.com/hari-lr/Preference-and-Perception-of-Decision-Making". Replication on Social Science Reproduction platform available at: https://doi.org/10.1525/collabra.74817
toc: true
number-sections: true
bibliography: references.bib
format: pdf
---

@@

[@sec-data] of this report aims to discuss the characteristics of the Study 2 data set examined in addition to the methods of cleaning applied to get workable data for this report. This report’s [@sec-results] highlights trends discovered through graphical analysis in tandem with statistical analysis of the preference and perceived competence responses using t-tests and p-values to determine statistical insignificance. [@sec-discussion] notes possible analytical limitations and measurement errors in the data sets in addition to overall insights of the report’s analysis. Specific discussion will surround the validity of assigning utilitarianism as a trait of men in addition to addressing whether or not there are differences in decision-making approaches based on gender. [@sec-future] aims to explore further research that could be conducted in this field based on the findings presented in this report.
